Presentation Title

### 2017-08-08 paper/s2-related.tex
Give paper a structure

\chapter{Problem description}
\label{ch:problem}

From the Introduction, we saw that early blockchain systems face a scalability problem.
In particular, the use proof-of-work is unlikely to reach a transaction rate suitable for ubiquitous use.
Many attempts to fix the scalability problem exist in academia as well as the industry.
In this chapter, we describe the related work in the form of a mini taxonomy and identify areas for improvement and limitations.
Then we state our research question which aims to overcome some of the limitations.

\section{Related work and mini taxonomy}
\label{sec:taxonomy}

Blockchain research has seen a surge in recent years from both the industry and academia,
this resulted in a myriad of blockchain systems with different approaches to scalability.
To understand the current state-of-the-art,
we classify various blockchain systems by their scalability approach.

\subsection{Early blockchain systems}
This category represents the baseline,
which are systems with a probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
The typical examples are proof-of-work based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, nodes compete in solving puzzles.
The first node solves the puzzle has the privilege to create a new block.
The level of consensus of a block containing many transactions is determined by how deep it is in the Bitcoin blockchain,
also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.

The advantage of this approach is that it can be used in a large network.
In fact, prior to Bitcoin, there was no internet-scale consensus protocol.
Bitcoin is also fault-tolerant because attackers can not out pace honest users in finding new blocks unless they have a majority of the hash power.
As long as the majority is honest and reasonable measures are taken to prevent the selfish mining attack~\cite{eyal2014majority}.
The disadvantage, however, is that transactions are never in consensus with a probability of 1---no consensus finality.
Hence double spending is possible for transactions that do not have a large number of confirmations.
Furthermore, as we mentioned in the Introduction,
the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.
Thus early blockchain systems do not achieve horizontal scalability.

% Our system significantly improves upon Bitcoin and other classical blockchain systems in performance, scalability and consensus finality.
% The results described in \Cref{ch:analysis} and \Cref{ch:implementation}, show that we have horizontal scalability,
% where more nodes result in more global throughput.
% Further, we do not have the aforementioned probabilistic behaviour,
% once some consensus result is decided, it cannot be orphaned, thus our consensus is final.
% The leadership election is also not ideal in classical blockchain systems.
% Mining can be seen as a technique to elect a single leader.
% The leader has full control of what goes into the block thus it may selectively censor transactions.
% We use ACS, so as long as the CP block is in $n - 2t$ nodes, it is guaranteed to be in consensus.

% However, the security aspect falls short of the ``honest majority'' security model that classical blockchains claim to 
% have\footnote{Recently it was shown that doing selfish-ming would give the adversary an unfair advantage when she only controls 25\% of the mining power~\cite{eyal2014majority}}.
% Our system risks going into erroneous state if the inequality $n \ge 3t + 1$ is not satisfied.
% Classical blockchain systems also have an incentive mechanism, thus they do not depend on altruistic nodes and encourages participation.
% Our system on the other hand does not have an incentive mechanism because we make no assumptions on the application.

@@

% Our system can be considered as the same as these types of blockchains but with a lightweight consensus protocol.
% Consensus might not be applicable in all applications.
% But we believe it is important for detecting and preventing fraud.
% The example in~\Cref{fig:trustchain-bad} on page~\pageref{fig:trustchain-bad} demonstrates this.
% If $b$ makes a fork and $a$ and $c$ have no way to communicate (e.g. the adversary may control parts of the network) ,
% then $c$ is tricked to believe that her transaction with $b$ is valid.
% Only when $c$ sees a conflicting chain is she able to tell that the transaction is invalid.
% But $c$ does not know the true end-of-chain of $b$, thus she can never know whether her transaction is valid.
% This is not possible in our system because $b$ cannot convince $c$ unless he can compute exponential time algorithms
% (this is finding the second preimage for a hash function).

% However, consensus and validation comes at a cost that do not exist in Tangle, Corda or the original TrustChain.
% Our transaction rate is affected by the validation protocol in the worst case scenario as we saw in~\Cref{sec:evaluation}.

\section{Research question}

We saw in~\Cref{sec:taxonomy} that the majority of the systems cannot achieve horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
To the best of our knowledge, only two systems---Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}---has experimentally demonstrated horizontal scalability.
However, these techniques rely on sharding, thus the performance highly depends on transaction characteristics and the shard size parameter because inter-shard transactions are slow.
Furthermore, all the systems described in~\Cref{sec:taxonomy} are complete blockchain systems designed for a concrete application.
We wish to design a blockchain consensus protocol that can be used in many applications.
For example recording uploads and downloads between peers in Tribler~\cite{pouwelse2008tribler, multichain} and decentralised market\footnote{\url{https://github.com/Tribler/tribler/blob/devel/Tribler/community/tradechain/__init__.py}}.
Hence our research question is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant, scalable and can reach global consensus?}
\end{displayquote}

In order to make sense of our research question, we must first define \emph{blockchain consensus protocol}.
Typical blockchain systems are application specific.
For example, the application in Bitcoin (any many of its derivatives) is digital cash, the application in Namecoin is domain name registration~\cite{namecoin} and the application in Siacoin is cloud storage~\cite{siacoin}.
Underneath these applications lies the blockchain consensus protocol which has the goal of reaching consensus on transactions or state changes.
In the case of Bitcoin, it is proof-of-work (PoW).
It is not concerned with the structure of the transactions,
it works by simply treating transactions as a blob of data and hashes them with the previous block.
In this work, we focus on the blockchain consensus protocol rather than any specific application.
Because it is the scalability bottleneck and is necessary for any blockchain based application.
% Also, it should be possible to build any kind of application on top our system.
% We do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

In the remainder of this section, we expand on our research question and visit each of our requirement in detail.
At the end of this section, we describe some issues that we do not consider as a part of our design,
which is the result of not focusing on any specific application.

\subsection{Global consensus}

% Early blockchain systems use PoW as the consensus algorithm,
% but consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
% consensus algorithms have existece since the 80s~\cite{pease1980reaching, lamport1982byzantine}.
% The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
% The authors show that running PBFT in Network File System (NFS) was only 3\% slower than the standard unreplicated NFS.
% Since then, research in this area picked up pace and many more algorithms are introduced, for example Q/U~\cite{abd2005fault} and Zyzzyva~\cite{kotla2007zyzzyva}.
% With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
% These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

The first objective is to reach consensus on a global \emph{state} by building on top of decades of Byzantine consensus protocol research~\cite{pease1980reaching, lamport1982byzantine, castro1999practical, miller2016honey}.
Having consensus is essential in blockchain systems.
It stops many types of malicious activities because agreed state must have the consent of the honest nodes in the network.
We emphasise the word state because in contrary to traditional blockchains,
it does not necessarily mean the set of all transactions that have ever happened.
The state can be a verifiable representation of all the transactions.
As an extreme example, a single digest of the complete history can represent the state.
It is even verifiable as long as there are nodes that store the history.

% Our approach is to combine the vast literature in Byzantine fault tolerance research with blockchain technology,
% and introduce a new consensus model to record the global state.

\subsection{Security and fault-tolerance}

Our system should be unaffected in the presence of powerful adversaries.
In particular, adversaries are Byzantine meaning that they can have arbitrary behaviour.
Thus anything is possible from simply omitting messages to colluding with each other in order to undermine the whole system.
This aspect usually comes for free when using a Byzantine fault-tolerant consensus algorithm.

There is another aspect of fault tolerance that is transaction verifiability.
All transactions must be eventually verifiable to maintain system integrity.
Further, the validation result must be consistent.
For example, if two different honest nodes attempts verify the same transaction,
it cannot be the case that one node thinks that the transaction is valid but the other thinks it is invalid.

% Recall that it is not neccessary to reach consensus on all the transactions in order to record the state.
% But when using some digest (or a set of digets) to represent the state, it is also important for the transactions to be verifiable.
% Otherwise adversaries could simply store invalid transactions in the state and they would never be detected.

\subsection{Performance and scalability}

The last but not least, the final objective is horizontal scalability.
We wish to see the performance (global transaction rate) increase as more nodes join the network.
BitTorrent~\cite{cohen2003incentives} is an example of such a system,
where peers interact with each other to exchange files without any global bottleneck.

Early blockchain systems may run in a network of thousands of nodes, but the performance does not scale.
On the other hand, as we will see in~\Cref{sec:acs-background}, Byzantine consensus algorithms perform well but only when in a small network.
In this work, our goal is to overcome the limitations of early blockchain systems and Byzantine consensus algorithms to create a horizontally scalable blockchain.

\subsection{Limitations}
Our work aims to significantly lower the transaction bound.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain consensus protocol to the application layer.
For example, social network based Sybil defence mechanisms use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

For the same reason, we do not explicitly consider spam or denial of service attacks.
Without a concrete application, it is difficult to distinguish a super active user from an attacker.

% Scalability is indeed one of the key challenges we face in blockchain systems today.
% Bitcoin~\cite{bitcoin}, the largest permissionless\footnote{Explain permissionless} blockchain system
% in terms of market capitalisation~\cite{bitcoinmarketcap} has a maximum transaction rate of merely 7 transaction per second (TX/s).
% This is due to the consensus mechanism in Bitcoin, namely proof-of-work (PoW),
% miners can only create new blocks every 10 minutes and every block cannot be larger than 1 megabyte.
% Payment processors in use today such as Visa can handle transaction rates in the order of thousands~\cite{visa}.
% While Bitcoin may be a revolutionary phenomenon, it clearly cannot be ubiquitous in its current state.

% An different approach is to not reach global consensus at all.
% For instance in TrustChain~\cite{multichain} and Tangle~\cite{tangle},
% nodes in the network only store their personal ledger.
% Since consensus is left out, nodes can perform transactions as fast as their machine and network allows.
% The downside of this approach is that it cannot prevent fraud (it is possible to detect fraud).
% To examplify, a malicious node Mallory may claim she has 3 units of currency to Alice,
% but in reality Mallory already spent all of it on Bob.
% If there is no global consensus and Bob and Alice never communicate,
% then the 3 units that Alice is about to receive is nonexistent.

% The scalability property of TrustChain and Tangle are exceptionally desirable.
% The global consensus mechanism of Bitcoin and many other blockchain systems are also worthwhile for detecting or preventing fraud.
% These two properties may seem mutually exclusive, but in this work, we demonstrate the opposite.
% Specifically, we answer the following research question in the affirmative.
% \emph{Is it possible to design a blockchain fabric that can reach global consensus on the state of the system 
% and also scalable?} We define scalability as a property where if more nodes join the system, then the transaction rate should increases.
% % this is not completely true, there's a cap

>>>>

\section{Background and Related Work}
% give background on ACS
% give background on TrustChain?

\subsection{Background on asynchronous subset consensus}
\label{sec:acs-background}

ACS is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{definition}
\label{def:acs}
\textbf{\emph{Asynchronous subset consensus}}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Totality:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resilience when compared to other consensus algorithms.
For instance, Hyperledger and Tendermint uses a variant of Practical Byzantine Fault Tolerance (PBFT)~\cite{castro1999practical} as their consensus algorithm.
In PBFT, a leader is elected, if the leader is malicious but follows the protocol, then it can selectively filter transactions.
In contrast, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.
Thus, if some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
For a detailed description of ACS, we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.
To understand the remainder of this work, the knowledge of~\Cref{def:acs} is sufficient.

The main drawback with ACS and also Byzantine consensus algorithms is the high message complexity.
Typically, such protocols have a message complexity of $O(n^2)$, where $n$ is the number of parties.
Hence, it may work with a small number of nodes,
but it is infeasible for blockchain systems where thousands of nodes are involved.

% The literature on Byzantine consensus and atomic broadcast is rich, some noteable ones include TODO.
% Thus in the ETC consensus protocol, we assume there exist an "off-the-shelf" Byzantine consensus algorithm which we can use
% (in our implementation we use HoneyBadgerBFT and motivate our choice in TODO).

% In our case, every node do not propose some arbitrary data, but a set of CP blocks.
% Thus the result of the consensus is the set union of all the legitimate proposals.

@@
